Andres Karjus

### 2019-03-01 index.Rmd
poster thumbnail

<div style="float: left; width: 60%; height: 200px; padding-right:10%; overflow: hidden">

- Poster to be presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an online [version with interactive plots](https://andreskarjus.github.io/isle_poster).

>>>>

<div style="float: left; width: 60%; height: 200px; padding-right:10%; overflow: hidden">
<a href="https://andreskarjus.github.io/isle_poster"><IMG SRC="poster_thumbnail.png" ALIGN="left" BR CLEAR="left" style="margin-left:10px; float: right;" /></a>

- "Modelling lexical interactions in diachronic corpora": a poster to be presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an online [version with interactive plots](https://andreskarjus.github.io/isle_poster).
